VariantSpark: Population Scale Clustering of Genotype Information

### 2015-11-26 doc/publications/journal2014/paper.tex
add r time

%% Use of \listoftables is discouraged.
%%
\section*{Tables}
\label{fivewaycomparison}
\begin{table}[h!]
\caption{The resource consumption of the six compared methods as well as the accuracy measured as \ARI{} on chromosome 22.}
      \begin{tabular}{|c|ccc|ccc|c|c|}
        \hline
           Tool &  \multicolumn{3}{ c |}{Pre-processing} & \multicolumn{3}{ c |}{Clustering} & Accuracy \\
& threads & memory & time  &threads & memory & time  & \\
  \hline
\variantSpark{}	& 8	& 32	& 2min 58sec	& 8	& 32	& 1min 20sec	& 0.84	\\ 
{\sc ADAM}		& 8	& 32	& 12min 48sec	& 8	& 32	& 1min 52sec	& 0.84	\\
Hadoop		& 8	& 32	& 14min 22sec	& 8	& 32	& 14min 23sec	& 0.84	\\
R			& 1	& 32	& 67min		& 8	& 32	& 7min 25sec	& 0.84	\\
Python		& 1	& 32	& 92min		& 8	& 32	& 11min 29sec	& 0.84	\\
{\sc Admixture}	& 1	& 32	& 10min 8sec	& 8	& 32 & 8min 19sec	& 0.25	\\
  \hline
      \end{tabular}
\end{table}

>>>>

%% Use of \listoftables is discouraged.
%%
\section*{Tables}
\label{fivewaycomparison}
\begin{table}[h!]
\caption{The resource consumption of the six compared methods as well as the accuracy measured as \ARI{} on chromosome 22.}
      \begin{tabular}{|c|ccc|ccc|c|c|}
        \hline
           Tool &  \multicolumn{3}{ c |}{Pre-processing} & \multicolumn{3}{ c |}{Clustering} & Accuracy \\
& threads & memory & time  &threads & memory & time  & \\
  \hline
\variantSpark{}	& 8	& 32	& 2min 58sec	& 8	& 32	& 1min 20sec	& 0.84	\\ 
{\sc ADAM}		& 8	& 32	& 12min 48sec	& 8	& 32	& 1min 52sec	& 0.84	\\
Hadoop		& 8	& 32	& 14min 22sec	& 8	& 32	& 14min 23sec	& 0.84	\\
R			& 1	& 32	& 34min 30sec	& 8	& 32	& 7min 25sec	& 0.84	\\
Python		& 1	& 32	& 92min		& 8	& 32	& 11min 29sec	& 0.84	\\
{\sc Admixture}	& 1	& 32	& 10min 8sec	& 8	& 32 & 8min 19sec	& 0.25	\\
  \hline
      \end{tabular}
\end{table}
